\documentclass[a4paper]{exam}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{listings}
\usepackage{xcolor} % Optional, for color
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{multirow}
\usepackage{array}
\usepackage{titling} % Required for the subtitle command
\usepackage{pythonhighlight}
\usepackage{graphicx}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray}, % Adjust font size and color
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left, % Line numbers on the left
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    firstnumber=1 % Start line numbers at 1
}


\lstset{style=mystyle}


\setlength{\droptitle}{-1.5in} % Adjust this value to decrease the spacing above the title

\title{MGMT 323 Supply Chain Management\\
Activity 1}

\author{Syed Ahad Ali\\
sa07753\\
L1}


\date{\today}

\printanswers % This command enables the display of answers


\begin{document}

    \maketitle
    % \vspace{-3cm} % Adjust this value to decrease the spacing below the title

    \begin{center}
        \textbf{Fall 2024}\\
        \textbf{Habib University}\\
        \textbf{Dhanani School of Science \& Engineering}\\
    \end{center}

    % \vspace{1cm} % Adjust this value to decrease the spacing below the title

    \begin{questions}
        \question{Why K\&N's has organized everything in house right from the beginning (acquiring eggs) all the way down to the final product placement at retail stores (raw chicken meat, frozen products etc.) ?}
        \begin{solution}
            The reason for that is that K\&N's is a vertically integrated company. A vertically integrated company is one that controls multiple stages of the supply chain. This means that K\&N's has control over the entire process from acquiring eggs to the final product placement at retail stores. This allows K\&N's to have more control over the quality of the product, the cost of production, and the efficiency of the supply chain. By having control over the entire process, K\&N's can ensure that the product meets their high quality standards, that the production process is cost-effective, and that the supply chain is efficient. This is why K\&N's has organized everything in-house right from the beginning.
        \end{solution}

        \question{Can you identify some initiatives taken by K\&N to halt or prohibit waste generation?}
        \begin{solution}
            \begin{itemize}
                \item K\&N's highly focuses on the health of upto two generation earlier of chicken to reduce the risk of chicken dying and getting wasted.
                \item K\&N's uses nipple drinkers for freshly incubated chicks to reduce water wastage.
                \item Usage of high quality egg clamps to avoid handling of eggs by hand and reducing the risk of breakage.
                \item Temperature controlled trucks for transportation of freshly incubated chicks to reduce the chicks dying and getting wasted.
                \item Chicken raising in properly ventilated and temperature controlled sheds to reduce the risk of chicken dying and getting wasted.
                \item Usage of high quality feed and natural grain products to reduce the risk of chicken dying and getting wasted.
            \end{itemize}
        \end{solution}

        \question{ Can you find out some clues regarding the "Sustainability Initiatives" taken by K\&N? (Hint: Sustainability is comprised of three dimensions Economic (Profits), Social (People), Environmental (Planet).)}
        \begin{solution}
            \begin{itemize}
                \item Economic: K\&N's has invested in state-of-the-art technology and equipment to improve the efficiency of their production process and reduce costs which has helped them to generate profits and become a multinational company. This generates lots of employment opportunities and helps in the economic growth of the country.
                \item Social: K\&N's has a strong focus on the social sustainability of their business. They have implemented various initiatives to improve the welfare of their employees and the communities in which they operate such as the Khair-un-Nisa Eye Hospital, Karachi, established in 2016 and collaborating with Habib University to provide scholarships to deserving students.
                \item Environmental: In the above questions, there are a lot of initiatives taken by K\&N's to reduce waste generation and improve the sustainability of their business. These initiatives help to reduce the environmental impact of their operations and make their business more sustainable.
            \end{itemize}
            \begin{thebibliography}{9}
                \bibitem{Author1}
                \url{https://kandnsfoundation.org/}
            \end{thebibliography}
        \end{solution}

        \question{Can you guess about the competitive priorities for K\&N? What are they?}
        \begin{solution}
            The competitive priorities for K\&N's are quality, cost, delivery, and flexibility. K\&N's is known for its high-quality products, which is one of the main reasons why customers choose K\&N's over other brands. K\&N's also focuses on cost, delivery, and flexibility to meet the needs of their customers and stay competitive in the market. By focusing on these competitive priorities, K\&N's has been able to grow and become a successful company.
        \end{solution}
    \end{questions}    
\end{document}
